\documentclass[12pt]{article}
\usepackage{titling}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum}
\usepackage[margin=1in]{geometry}

\input{~/.macros}

\hypersetup
{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}


\begin{document}

\title{Reasons}
\author{Jonah Mondragon}
\date{\today}
\PutTitle{Freshman Fitness Period 4}

\section*{10 things that require no talent, and will lead to success}
\begin{multicols}{2}
    \begin{enumerate}
        \item{Being On Time}
        \item{Work Ethic}
        \item{Effort}
        \item{Body Language}
        \item{Energy}
        \item{Attitude}
        \item{Passion}
        \item{Being Coachable}
        \item{Doing Extra}
        \item{Being Prepared}
    \end{enumerate}
\end{multicols}

\section*{Why passion will make me successful this year}
\doublespacing
\paragraph~
I am full of passion; along with it comes the synonym of love; I'm in love.
Love with another, but more importantly; love with myself.
I've been pushing myself for a few months now, and before I was experiencing a certain unensuring productivity.
This feeling of passion, of \textit{love}, makes me an unrelenting force of nature, and my partner only aides that.
It's human nature to perform better while confident, what makes one more confident then the feeling of love? 
Being completely drowned in nothing but positivity; even the negativity becomes positive, whether it be because of comedy, or as a reminder of the positivity.

Passion fills my hand, everything I touch becomes enamored; blesséd.
I'll have no issues waking up every morning, getting after it with the workouts, \textit{everyday}, and studying hard 
    (this, however, does \textit{not} include my school studies for this school year, at the time of writing, because I procrastinated on it diligently; next year, for sure, I'll have a better run).
I have a passion for my girl, and for programming; it's gotten to the point that {\color{blue}\underline{\href{https://www.geeksforgeeks.org/c-plus-plus/}{C++}}} has become my native tongue.
These two, aforementioned, make up my \textit{drive}, as discussed in a previous assignment, when I wake up they're all I think about; that and the workout ahead.
The average American, who exercises; does it with intensity, rendering them useless for the majority of the week, meaning three days a week off ball-busting exhaustion and four for recovery.
Many think this is a smart approach, but they couldn't be further from the truth; consistent excercise everyday going half intensity will give you better and longer lasting 
    results.\footnote{This is proven by several sources, the prominent among them is \href{https://www.healthline.com/health/exercise-fitness/working-out-every-day#benefits}{here}}
These are the three that matter, truly; my passion, my girl, and programming.

\end{document}
