\documentclass[12pt]{article}
\usepackage{titling}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage[shortlabels]{enumitem}
\usepackage[margin=1in]{geometry}

\newcommand{\PutTitle}[1]
{
    \begin{center}
        {\huge\bfseries\thetitle}\\
        by \theauthor\\
        \thedate\\
        #1        
    \end{center}
    \hrule
    \vspace{2ex}
}

\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\parindent{24pt}

\hypersetup
{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\begin{document}

\title{Meso Inventions that Changed the World}
\author{Jonah Mondragon}
\date{\today}
\PutTitle{World History Period 7}

\doublespacing

The people in my group are Jonah Mondragon, Izaiah Gonzales, Analy Espinoza,
Elizandra Martinez, Marixa Enriquez.

\section{The Wheel}
    \begin{enumerate}[A.]
        \item{The wheel was an invention designed as a luxurious form of
            transportation for the wealthy, but was also used for irrigation.}
        \item{The wheel is used by almost every human, whether it's for a bike,
            car, or even in machines.}
    \end{enumerate}

\section{The Chariot}
    \begin{enumerate}[A.]
        \item{The chariot was used for personal transportation and then was
            modified in warfare, sport, and general use.}
        \item{Chariots have evolved into new forms of transportation, cars
            which are still used today.}
    \end{enumerate}

\section{The Plow}
    \begin{enumerate}[A.]
        \item{The plow was used as an agriculture tool that the Sumerian's
            invented.}
        \item{The plow has evolved, and now we have the automatic trucks that
            auto plants seeds.}
    \end{enumerate}

\section{Writing/cuneiform}
\begin{enumerate}[A.] 
    \item{Writing allowed the Mesopotamians to keep track of goods that were
        bought and sold.}
    \item{Writing is still used today for the same purpose as well as to record
        history and stores; but has evolved to record information with
        computers.}
\end{enumerate}

\section{Mathematics}
\begin{enumerate}[A.]
    \item{Mathematics was used by the Mesopotamians to document the count of
        livestock, and document prices for goods; mathematics also allowed the
        Mesopotamians to solve irrigation problems and produce architecture.}
    \item{Mathematics today is still used for architecture, but we have evolved
        it to the point that it's our main tool for solving problems relating
        to physics; it even ranges to philosophy and space travel; mathematics is
        the backbone of engineering.}
\end{enumerate}

\section{The Sailboat}
\begin{enumerate}[A.]
    \item{Sailboats were important to the Mesopotamians as they allowed for
        faster and more efficient travel than that which was around bodies of
        water.}
    \item{Sailboats today aren't used for the ease of travel, but the
        inexpensive transportation of bulk goods.}
\end{enumerate}

\section{Mass-produced Pottery}
\begin{enumerate}[A.]
    \item{Useful to the Mesopotamians because it started the creation of the
        turning wheel, and would later help them produce other useful items.}
    \item{Used today in the way of mugs, containers, vases, etc....}
\end{enumerate}

\section{Textile Mills}
\begin{enumerate}[A.]
    \item{Useful to the Mesopotamians because it helped them weave fabric for
        clothing, and it’s creation was used to form larger organizations and
        it became the predecessor of modern manufacturing companies.}
    \item{They are still used today in yarn, fabric, woven and nonwoven textile
        manufacturing.}
\end{enumerate}

\section{Mass-produced Bricks}
\begin{enumerate}[A.]
    \item{Useful to the Mesopotamians because they could produce large amounts
        of bricks, and were easily produced to build more.}
    \item{Used today because they are an easier, reliable and more available
        resource than stone.}
\end{enumerate}

\section{Metallurgy}
\begin{enumerate}[A.]
    \item{Metallurgy was important to the Mesopotamians because the Sumerians
        metallurgists were some of the earliest people to use copper to make
        useful items, ranging from spearheads to chisels and razors, according to
        the Copper Development Association. They also used furnaces heated by reeds and
        controlled the temperature with a bellows that could be worked with their hand
        or feet.}
    \item{Metallurgy is still used by forming the backbone of modern aircraft,
        automobiles, trains, ships and endless recreational vehicles.}
\end{enumerate}

\section{Agriculture, Irrigation, Hydrolic engineering}
\begin{enumerate}[A.]
    \item{Agriculture and irrigation was important to the Mesopotamians because the
        Mesopotamians learned to control the flow of water from the river and used
        it to irrigate crops.}
    \item{Irrigation and Agriculture is still used on improving crop growth and
        quality.}
\end{enumerate}

\section{Time}
\begin{enumerate}[A.]
    \item{The Mesopotamians developed the concept of time, dividing time
        units into 60 parts, which  eventually led to 60- minutes and 60-
        minutes hours.}
    \item{Today, we take our global system of timekeeping largely for granted:
        24 time zones rippling serenely outward from Greenwich; a year of 12
        months, divided into 52 weeks, recognized from San Francisco to Shanghai;
        the much-loathed biannual leap of daylight saving time}
\end{enumerate}

\section{Astronomy and Astrology}
    \item{Astrology, a type of divination that involves the forecasting of
        earthly and human events through the observation and interpretation of
        the fixed stars, the Sun, the Moon, and the plants.}
    \item{The branch of science which deals with celestial objects, space and
        physical universe as a whole.}
\end{enumerate}

\section{The Map}
\begin{enumerate}[A.]
    \item{Why was the invention important to the Mesopotamians?  The invention
        of the map was important to the Mesopotamians because it would show the
        Akkadian region of Mesopotamia (present-day northern Iraq).}
    \item{How is the invention still used Today?  The invention of the map is
        still used today for showing us present information of the world in a
    more simple way.}
\end{enumerate}

\section{Urban civilization}
\begin{enumerate}[A.]
    \item{Why was the invention important to the Mesopotamians?  Urban
        Civilization was important to the Mesopotamians because it made it
        possible for them to feed more animals and people, helped them learned to
        trade, and helped them learn the concepts of the development of taxes.}
    \item{Urban Civilization is still used today such as the Aztec Empire or
        the Aztec Civilization which was a highly developed socially,
        intellectually and artistically civilization.}
\end{enumerate}

\end{document}

