\documentclass[12pt]{article}
\usepackage{titling}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}

\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\parindent{24pt}

\hypersetup
{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\begin{document}

\doublespacing

\begin{titlepage}
    \begin{center}
        \vspace*{1.5in}
        {\huge\bfseries{Who Am I? DRAFT \#1}}\\
            {\bfseries{by Jonah Mondragon}}\\
            World History Period 7\\
            \today
    \end{center}
\end{titlepage}

\section*{Part A: All About Me}

I was born on November 2, 2005 at Taos Holy Cross Hospital.
I had managed to wrap my neck in the umbilical cord such that I had to be removed from my 
    mother's stomach by c-section.
Part of my conceptualization involved a custody battle between my mother and father.
This custody battle forced my father to sell a 1968 Chevrolet Camaro Super Sport
    in order to pay for his lawyer, I would be driving it around today had he not sold it.
Long story short, my father won custody over me and I have lived out the first fifteen years of my 
    life in a large house next to the {\color{blue}\underline{\href{https://www.taoscountryclub.com/}{Taos Country Club}}} with him.

I bear crawled before I crawled normally and, according to my father, ran before I walked.
In the courtroom where my parents allowed their lawyers to fight for the right of raising me,
    it was the first time I'd been able to see my father in months; %more precise?%
    I heard his voice and ran down the courtroom walkway to him as soon as I was out of 
    my mother's hold, I was three years old. %fact check this>
The reason for this custody battle boils down to the fact that my mother  ``kidnapped'' me in the
    attempt to extricate me from the ``abusive'' hands of my father (the exact details of this don't
    have the need to be related here, but know that all is fine with my situation now).
My mother obtained possession of me without the legal authority to do so a handful of times, the
    exact chronological order of these events is vague at best and the only way to decide of it
    exactly would be to scrounge through court transcripts and other documents, an endeavor
    that I don't want to partake in as I have exerted enough mental energy throughout my lifetime
    being concerned with my early childhood.

The initial arrangement of my custody situation was one that most kids in a situation similar to mine
    have had, shared custody; my father would have me for a week, then my mother would have me for a week
    (perhaps it was some other period of time, I can't remember).
Of the time spent with my father I have quite literally no recollection, they were
    spent either with my father's ex wife, a woman whom I've grown to know as my grandma or playing video
    games; I don't remember going to school, it must have been before I was enrolled in anything beyond a
    daycare, again my memories overlap quite a bit chronologically.
Come to think of my  mother and have never married.

A woman named Dawn (I believe "Dawn" is short for "Dawna," I know, quite the truncation) at one point was
    my mother's landlord


\end{document}
