\documentclass[12pt]{article}
\usepackage{lipsum}
\usepackage{titling}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{scrextend}
\usepackage[margin=1in]{geometry}

\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}

\hypersetup
{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\newcommand{\PutTitle}[1]
{
    \begin{center}
        {\huge\bfseries\thetitle}\\
        by \theauthor\\
        \thedate\\
        #1
    \end{center}
    \hrule
}

\begin{document}
\title{Route 66 Test}
\author{Jonah Mondagon}
\date{\today}
\PutTitle{New Mexico History Period 3}

\pagestyle{headings}

\doublespacing

\begin{enumerate}
    \item{\textit{Route 66 ran between which two United States cities and states?}}
        \begin{addmargin}[24pt]{0in}
            Route 66 ran between St. Louis, Missouri and Chicago, Illinois.
        \end{addmargin}
    \item{\textit{What is the name of the famous motel on Rt. 66 in Tucumcari, New Mexico, that is known for its neon sign? Tucumcari Tonight!}}
        \begin{addmargin}[24pt]{0in}
            The name of the famous motel on Rt. 66, in Tucumcari, New Mexico; is \textit{Blue Swallow Motel}.
        \end{addmargin}
    \item{\textit{2 Part Question: Which Avenue in Albuquerque today used to be Rt. 66? And which Interstate Highway that goes through New Mexico now took over Rt. 66's route?}}
        \begin{addmargin}[24pt]{0in}
            \begin{itemize}
                \item{The avenue of Albuquerque, today, that used to by Rt. 66 is Central Avenue.}
                \item{Five interstate highways replaced route 66; I-55 from Chicago; I-44; I-40; I-15; I-10.}
            \end{itemize}
        \end{addmargin}
    \item{\textit{Which New Mexico city gets a shout out in (Get Your Kicks on) Rt. 66?}}
        \begin{addmargin}[24pt]{0in}
            Gallup, New Mexico is mentioned in the song {\color{blue}\underline{\href{https://www.youtube.com/watch?v=9nuDE1SJlPo}{\textit{(Get Your Kicks On) Route 66}}}}.
        \end{addmargin}
    \item{\textit{Which New Mexico town was NOT on Rt. 66?}}
        \begin{addmargin}[24pt]{0in}
            Hatch, New Mexico is a town NOT along Route 66.
        \end{addmargin}
    \item{\textit{Originally, from 1926 to 1937, why did Rt. 66 go through Santa Fe?}}
        \begin{addmargin}[24pt]{0in}
            Previous New Mexican governor {\color{blue}\underline{\href{https://www.nga.org/governor/arthur-thomas-hannett/}{Arthur. T. Hannett}}} lost his re-election; as a spite method against other New Mexican politicians, he decided to reroute Route 66 to go through
               Albuquerque instead of Santa Fe.
            This undertaking was initiated so late during his position as governor that it was only bad weather that prevented Hannett's successor from stopping the reroute; it was impossible to get into contact with the crew.
            (See source \#\ref{reroute})
        \end{addmargin}
    \item{\textit{First, next to railroad stations and then later on Rt. 66, Fred Harvey opened America's first chain restaurants and hotels, which were called?}}
        \begin{addmargin}[24pt]{0in}
            America's first chain of restaurants and hotels were called \textit{Harvey Houses}.
        \end{addmargin}
    \item{\textit{In the late 1930s a lot of 'Okies' from Oklahoma passed through New Mexico on Rt. 66 to get to California during what environmental disaster?}}
        \begin{addmargin}[24pt]{0in}
            {\color{blue}\underline{\href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4015056/}{The Dust Bowl}}} was an environmental disaster that forced ``Okies'' to migrate, through New Mexico, to California; during the late 1930's.
        \end{addmargin}
    \item{\textit{What famous hotel in Gallup, which is still open today, was where many movie stars stayed when they were filming Westerns in New Mexico?  Bonus points: Name 3 famous actors who stayed there?}}
        \begin{addmargin}[24pt]{0in}
            {\color{blue}\underline{\href{https://www.nps.gov/nr/travel/route66/el_rancho_hotel_gallup.html}{El Rancho Hotel}}} is a hotel that many movie stars stayed at while filming Westerns in New Mexico.
            Three of the famous actors that have stayed in the El Rancho Hotel are; {\color{blue}\underline{\href{https://www.johnwayne.com/}{John Wayne}}}; 
                {\color{blue}\underline{\href{https://www.biography.com/actor/katharine-hepburn}{Katherine Hepburn}}}; {\color{blue}\underline{\href{https://www.newworldencyclopedia.org/entry/Spencer_Tracy}{Spencer Tracy}}}.
        \end{addmargin}
    \item{\textit{Segments of Rt. 66 are still alive! On a stretch in the mountains on the Eastside of Albuquerque, if you drive your car at 45 MPH over some grooves in the road, which song can be heard?}}
        \begin{addmargin}[24pt]{0in}
            Driving at 45mph on a specific stretch of Route 66, a part that still exists today; the driver can hear the tune of {\color{blue}\underline{\href{https://www.youtube.com/watch?v=TRUjr8EVgBg}{America the Beautiful}}}.
        \end{addmargin}
\end{enumerate}

\newpage

\section*{Sources\footnote{All sources were accessed at the date of this document.}}
\subsection*{External Information}
\begin{enumerate}
    \item{\url{https://getaway.10best.com/13451472/where-does-route-66-start-and-end}}
    \item{\url{https://www.theroute-66.com/towns.html}}
    \item{\url{https://www.theroadwanderer.net/66NMex/santafe.htm}}\label{reroute}
    \item{\url{https://www.okhistory.org/publications/enc/entry.php?entry=OK008}}
    \item{\url{https://abcnews.go.com/blogs/headlines/2014/10/route-66-adds-singing-road-as-speeding-deterrent/}}
\end{enumerate}
\subsection*{Hyperlinks (In order of appearance)\footnote{Hyperlinks are the blue clickable text seen throughout this document; but that aren't directly written as a web address.}}
\begin{enumerate}
    \item{\url{https://www.youtube.com/watch?v=9nuDE1SJlPo}}
    \item{\url{https://www.nga.org/governor/arthur-thomas-hannett/}}
    \item{\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4015056/}}
    \item{\url{https://www.nps.gov/nr/travel/route66/el_rancho_hotel_gallup.html}}
    \item{\url{https://www.johnwayne.com/}}
    \item{\url{https://www.biography.com/actor/katharine-hepburn}}
    \item{\url{https://www.newworldencyclopedia.org/entry/Spencer_Tracy}}
    \item{\url{https://www.youtube.com/watch?v=TRUjr8EVgBg}}
\end{enumerate}

\end{document}
