\documentclass{article}
\usepackage{longtable}
\usepackage{array}
\usepackage{titling}
\usepackage[margin=1in]{geometry}

\paperwidth = 8in
\paperheight = 11in

\renewcommand{\maketitle}
{
    \begin{center}
        {\huge\bfseries\thetitle \\ [0.5ex]}
        \theauthor \\ [0.5ex]
        \thedate \\  [0.5ex]
        English Period 8
        \vspace{1ex}
        \hline
    \end{center}
}

\pagestyle{empty}
\begin{document}

\title{Plus Minus Delta}
\author{Jonah Mondragon}
\date{February 19, 2021}

\maketitle

\begin{center}
    \begin{longtable}[c]{|m{1.9in}|m{1.9in}|m{1.9in}|}
        \hline
        Name & Plus & Minus \\
        \hline\hline
        Antonio Martinex
        &
        \begin{itemize}
            \item{The presentation design was appealing; the blue device used throughout marked a flare in the text.}
            \item{The speaker was quick to fix his enunciation errors.}
        \end{itemize}
        &
        \begin{itemize}
            \item{The information was disconnected from the images used.}
            \item{The speaker spent too much time thinking about what to say, rather than what was being said.}
        \end{itemize}
        \\
        \hline

        Joseph Gonzales
        &
        \begin{itemize}
            \item{The information was pertinent to the subject matter.}
        \end{itemize}
        &
        \begin{itemize}
            \item{The speaker had not only trouble enunciating his words, but did not make any effort to correct himeself.}
            \item{The presentation was bland, colorless and lacked visual appeal.}
        \end{itemize}
        \\
        \hline

        Jacob Kreigshauser
        &
        \begin{itemize}
            \item{The presentation was neatly formatted; there was a promenant use of object separation.}
            \item{The speaker enunciated his words very well.}
        \end{itemize}
        &
        \begin{itemize}
            \item{The images were uninspired and low quality.}
        \end{itemize}
        \\
        \hline

        Irene Cavaller-Garcia
        &
        \begin{itemize}
            \item{The presentation was prestine; the light brown hues blended will with the obvious palette-chosen images.}
            \item{The speakers enunciation was clear and concise, with a bit of an accent.}
            \item{A lot of time was put into formatting the text.}
            \item{The research done involving the subject matter was extinsive.}
        \end{itemize}
        &
        \begin{itemize}
            \item{The speaker read too fast to be easily interpreted.}
        \end{itemize}
        \\
        \hline

        Liliana Lujan
        &
        \begin{itemize}
            \item{The presentation by enunciation was well thought out.}
        \end{itemize}
        &
        \begin{itemize}
            \item{The speaker seemed to be disconnected with her words.}
        \end{itemize}
        \\
        \hline

        Ryen Ortega
        &
        \begin{itemize}
            \item{The enunciation was pristine.}
        \end{itemize}
        &
        \begin{itemize}
            \item{The presentation wasn't complete, only three conditions.}
            \item{The images were low quality.}
            \item{The presentation wasn't complete, only three conditions.}
        \end{itemize}
        \\

        \hline

        Elija Romero
        &
        \begin{itemize}
            \item{Involved image/information correlation.}
        \end{itemize}
        &
        \begin{itemize}
            \item{Severe lack in reader/oral connection; uninolved presentation (the images seems to have been unconserted)}
        \end{itemize}
        \\
        \hline
        Diego Cordova
        &
        \begin{itemize}
            \item{Information was well formatted and researched.}
        \end{itemize}
        &
        \begin{itemize}
            \item{Images were low quality and had uninvolved corelation.}
        \end{itemize}
        \\
        \hline
    \end{longtable}
\begin{center}

\end{document}
